HEP Software Foundation Community White Paper Working Group -- Detector Simulation

### 2018-03-01 CWP/papers/HSF-CWP-2017-07_detsim/latex/DetectorSimulation.tex
moved position of 2 references 18 and 19

Electromagnetic (EM) transport simulation is challenging as it occupies
a significant part of the computing resources used in full detector
simulation. More experimental data in the coming decade implies higher
statistics and this implies the need for large and accurate simulation
samples, which require both model accuracy and speed. Therefore the
physics models need to be improved for achieving higher accuracy and the
implementation of algorithms needs to be reviewed in order to optimise
performance. Significant efforts have been made in the recent past to
better describe the simulation of electromagnetic shower shapes, in
particular to model the H $\rightarrow \gamma \gamma $ 
signal accurately at the LHC. This effort is being continued with 
emphasis on reviewing the
models assumptions, approximations and limitations, especially at very
high energy, and with a view to improving their respective software
implementations. For LHC Run-1 simulation Geant4 version 9.4 was used
~\cite{1742-6596-331-3-032029}. For Run-2 significant improvements were introduced into the
bremsstrahlung, pair production and multiple scattering
further improving simulation of the EM shower shape
~\cite{1742-6596-396-2-022013}~\cite{1742-6596-513-2-022015}; these improvements
were made available in Geant4 9.5 and 9.6. For validation purposes, an
extended set of tests versus data has been developed for high, moderate
and low-energies using test-beam data and published thin target data.
Comparisons with low-energy EM models from the Livermore and Penelope
packages were also carried out.

>>>>

Electromagnetic (EM) transport simulation is challenging as it occupies
a significant part of the computing resources used in full detector
simulation. More experimental data in the coming decade implies higher
statistics and this implies the need for large and accurate simulation
samples, which require both model accuracy and speed. Therefore the
physics models need to be improved for achieving higher accuracy and the
implementation of algorithms needs to be reviewed in order to optimise
performance. Significant efforts have been made in the recent past to
better describe the simulation of electromagnetic shower shapes, in
particular to model the H $\rightarrow \gamma \gamma $ 
signal accurately at the LHC. This effort is being continued with 
emphasis on reviewing the
models assumptions, approximations and limitations, especially at very
high energy, and with a view to improving their respective software
implementations. For LHC Run-1 simulation Geant4 version 9.4 was used
~\cite{1742-6596-331-3-032029}. For Run-2 significant improvements were introduced into the
bremsstrahlung, pair production and multiple scattering,
further improving simulation of the EM shower shape 
~\cite{1742-6596-396-2-022013}~\cite{1742-6596-513-2-022015}; these improvements
were made available in Geant4 9.5 and 9.6. For validation purposes, an
extended set of tests versus data has been developed for high, moderate
and low-energies using test-beam data and published thin target data.
Comparisons with low-energy EM models from the Livermore and Penelope
packages were also carried out.
